\documentclass[11pt,letterpaper]{article}
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage{bbm}
\usepackage{fullpage}

\begin{document}

Zackery Field

ID: 23031734

CS 70, Summer 2013

Homework 1 

Problem 5 (7 Points)
\bigskip

\begin{enumerate}
\item[5a.] [3 points]

Theorem:
For all natural numbers n, if n is odd then $n^2 + 2n$ is odd.

Direct Proof:

It can be shown that $n^2$ is odd (for odd n), and $2n$ is even, and that the operation $odd + even$ always produces odd output.

Proof by contradiction ($n^2$ is odd, for odd n):

Assume $n^2 $ is even, for odd n, then $n^2 $ is divisible by only one even number, 2. It follows that if $n^2$ is divisible by 2, then $n$ must be divisible by $\sqrt{2}$, a contradiction since $n \in \mathbb{N}$

Direct proof($2n$ is even):

For any choice of $n$, $2n$, is divisible by 2. Therefore $2n$ is even. 

Direct proof ($even + odd = odd$):

For some numbers $a,b \in \mathbb{N}$, $(2a) + (2b+1)$ is of the form $even + odd$.

\begin{eqnarray}
(2a) + (2b+1) \\
= 2(a+b) + 1 \\
= 2n + 1, \: n \in \mathbb{N} \\
\end{eqnarray}
and, by definition, 2n+1 is odd.


\bigskip
\item[5b.][3 points]

Theorem:
For all natural numbers n, $n^2 + 7n + 1$ is odd.

Proof by cases:

Case 1(n is odd):

For n odd, it can be shown that $n^2 + 7n + 1$ is of the form $odd + odd + 1$ which is $odd$.

Proof by contradiction ($n^2$ is odd, for odd n):

Assume $n^2 $ is even, for odd n, then $n^2 $ is divisible by only one even number, 2. It follows that if $n^2$ is divisible by 2, then $n$ must be divisible by $\sqrt{2}$, a contradiction since $n \in \mathbb{N}$

Direct proof($7n$ is odd):

For any choice of $n$, $7n$, is not divisible by 2. Therefore $7n$ is odd. 
 
Direct proof ($odd + odd = even$):

For some numbers $a, b \in \mathbb{N}$, $(2a + 1) + (2b +1)$ is of the form $odd + odd$.

\begin{eqnarray}
(2a+1) + (2b+1) \\
= 2(a+b+1)  \\
= 2n, \: n \in \mathbb{N} \\
\end{eqnarray}
and, by definition, 2n is even.

Following directly from above, if $odd + odd = even$, then $odd + odd + 1 = even + 1$, and $odd + odd + 1 = odd$.

It was shown above that $n^2 + 7n + 1$ is of the form $odd + odd + 1$, proving the theorem for $n \: odd$.

Case 2 (n is even):

It can be shown that $n^2 + 7n + 1$ is of the form $even + even + 1$, for odd $n$.

Direct proof ($n^2$ is even):

If $n$ is even, then for some $m \in \mathbb{N} \: n = 2m$ 

\begin{eqnarray}
n^2 = (2m)^2 \\
= 4 * m^2
\end{eqnarray}
, and 4 is divisble by 2, so $n^2$ is even.

Direct proof (7n is even):

If $n$ is even, then for some $m \in \mathbb{N} \: n = 2m$ 

\begin{eqnarray}
7n = 7(2m) \\
\end{eqnarray}
which is divisible by 2, and is therefore even.

Direct Proof ($even + even + 1 = odd$):

For some numbers $a, b \in \mathbb{N}$, $(2a) + (2b) + 1 $ is of the form $even + even + 1$.

\begin{eqnarray}
(2a) + (2b) +1 \\
= 2(a+b) +1  \\
= 2n + 1, \: n \in \mathbb{N} \\
\end{eqnarray}
and, by definition, 2n+1 is odd.

It was shown above that $n^2 + 7n + 1$ is of the form $even + even + 1$, proving the theorem for $n \: even$.


\bigskip
\item[5c.] [3 points]

Theorem:
For all real numbers a,b, if $a+b \leq 10 $ then $a \leq 7$ or $b \leq 3$

Proof by contradiction:

Assume, if $a+b \leq 10 $ then $a > 7$ or $b > 3$.



\bigskip
\item[5d.] [3 points]

Theorem:
For all real numbers r, if r is is irrational then r+1 is irrational.

Proof:

\bigskip
\item[5e.] [3 points]

Theorem:
For all natural numbers n, $10n^2 > n!$.

Proof:


\end{enumerate}

\end{document}
